Milestone 2: Core results 01

### 2023-02-11 R_codeP01/reports/MS2_report02.Rmd
cv residuals

>>>>

### Mechanistic + Residuals -> proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_prolif.RData")
lc_residuals_771_p_a <- report02_out(lc_obj_residuals_771_p_a)
```
### Mechanistic + Residuals -> proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_prolif.RData")
lc_residuals_771_p_m <- report02_out(lc_obj_residuals_771_prolif)
```
### Mechnaistic + Residuals -> ROR-proliferation score (additive)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_RORprolif.RData")
lc_residuals_ROR_p_a <- report02_out(lc_obj_residuals_771_RORprolif)
```
### Mechnaistic + Residuals -> ROR-proliferation score (multiplicative)
```{r}
load("/Users/anders/Documents/MASTER/Cancer/R_codeP01/instances/lc_obj_residuals_771_RORprolif.RData")
lc_residuals_ROR_p_m <- report02_out(lc_obj_residuals_771_RORprolif)
```
